Meesters TODO List

### 2023-04-18 Gedoen.tex
Overview 2.0
chap 2.4 and chap 4.2

\subsection{Chapter 1}
\begin{itemize}
	\item Het 1.4.21 reg gemaak. Moet nog deur gaan en seker maak ek het dit ander plekke reg.
\end{itemize}

\subsection{Chapter 2}
\begin{itemize}
	\item Het verbeteringe aangebring.
\end{itemize}

\subsection{Appendix}
\begin{itemize}
	\item $L_2$ in gesit.
\end{itemize}

>>>>

Het gefokus om eerder klein veranderinge te maak. So lyk dalk na min veranderinge maar het probeer mooi dink oor als. Daar is nog wat ek more aan gaan werk, maar is kleiner goed soos seker maak die references na equations/sections is als reg.
\subsubsection*{Section 2.4}
Het gefokus om die verduideliking te verbeter. Ek weet prof het gese die eigenvalue problem moet voor die differential equation van $T$ wees, maar ek het nie die volgorder verander nie. EK het gevoel dit gaan baie meer verander en dan mag ek dalk grooter foute maak. So e het dit gelos, en probeer die verduideliking reg maak.

Ek het dan van die klein veranderinge ook gemaak.

\subsubsection*{Section 4.1}
Het 'n eenvoudige inleiding gemaak wat section 2.4 link.

\subsubsection*{Section 4.2}
Aan die einde net die werk oor die pinned pinned beam by gesit. Het dit net gehou soos prof versuidelik het, en nog nie op die regte plek gesit nie.

Het ook goed in die begin wat dood getrek was uit gehaal

### 2023-04-18 files/Chapter2/generalvibrationmodel.tex
chap 2.4 and chap 4.2

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

@@

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.

\textcolor{red}{Due to this periodicity of these solutions for} the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions. This solution is called the constant solution.

A systematic approach to get the eigenvalues and eigenfunctions is given in \cite{VV06}. This is discussed in in Section 4.2. The following theorem is derived from \cite{VV06} and confirms the validity of our trial solutions for the eigenvalue problem.

\newtheorem{ThmVV06}{Theorem}
\begin{ThmVV06}
	If $\langle u \ \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. Also all eigenvalues less than $\alpha$ are simple eigenvalues. The solution $\langle 0, 1 \rangle$ is a constant solution of Problem T-1E.
\end{ThmVV06}

@@

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with $u(0)=u_{0}$, $u'(0)=u_{1}$.\\

@@

Similar to the example of the pinned-pinned beam in the previous section, substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that 
\begin{eqnarray}
	T''  + \lambda T = 0,
\end{eqnarray}
and there exists a $x \in V$ with $x \neq 0$ such that
\begin{eqnarray}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray}

@@

>>>>

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation,
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

@@

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.

Due to this periodicity of these solutions for the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions. This solution is called the constant solution.

A systematic approach to obtain the eigenvalues and eigenfunctions is given in \cite{VV06}. This is discussed in in Section 4.2. From \cite{VV06}, the following theorem can be derived and confirms the validity of our trial solutions for the eigenvalue problem.

\newtheorem{ThmVV06}{Theorem}
\begin{ThmVV06}
	If $\langle u, \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u, \phi\rangle = \langle\sin k \pi x, A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. If $\langle u, \phi\rangle$ is a constant eigenfunction of Problem T1-E, then  $\langle u, \phi\rangle = \langle 0, 1 \rangle$. Also all eigenvalues less than $\alpha$ are simple eigenvalues.
\end{ThmVV06}

@@

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with $u(0)=u_{0}$, $u'(0)=u_{1}$.

@@

Substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that 
\begin{eqnarray}
	T''  + \lambda T = 0,
\end{eqnarray}
and there exists a $x \in V$ with $x \neq 0$ such that
\begin{eqnarray}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray}

@@

\textcolor{red}{*************** Need to check everything below this ******************}

### 2023-04-18 files/Chapter4/ModalAnalysisTimo.tex
chap 2.4 and chap 4.2

The next step is to determine the solution of the general eigenvalue problem. The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example. A summary of the strategy is presented here.\\

@@

 This system has either the zero solution or infinitely many solutions. To ensure a non-zero solution, the determinant of the coefficient matrix $A$ of the system of equations is set equal to 0. The equation $\textrm{det}(A) = 0$ is called the frequency equation. The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.\\

 For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.\\

In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}. For $\lambda < \alpha$ the general solution reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$. For $\lambda > \alpha$, the general solution also reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$. For $\lambda = \alpha$, the general solution reduces to $\langle u , \phi \rangle = \langle 0, 1 \rangle$.\\

This is proved rigourously in \cite{VV06} and also proved Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.

>>>>

The next step is to determine the solution of the general eigenvalue problem. The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example. A summary of the strategy is presented here.

@@

 This system has either the zero solution or infinitely many solutions. To ensure a non-zero solution, the determinant of the coefficient matrix $A$ of the system of equations is set equal to 0. The equation $\textrm{det}(A) = 0$ is called the frequency equation. The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.

 For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.

\textcolor{red}{Die moet net op die regte plek gesit word.}

\textcolor{red}{**********************************************}

In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}. The authors  For $\lambda < \alpha$ the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k \cos(k \pi x) \rangle$. For $\lambda > \alpha$, the general solution also reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k  \cos(k \pi x) \rangle$. For $\lambda = \alpha$, the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle 0, 1 \rangle$.

This is proved rigourously in \cite{VV06} and also proves Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.

\textcolor{red}{**********************************************}
